QALY Comparisons - Energy Crisis Interventions

### 2023-11-01 minos/testing/QALY_comparison_energyCrises.Rmd
Added run_id to QALY_calculation outputs for plotting confidence. Improved script for comparing energy crises interventions, and added new script for QALY calculations on living wage intervention. Also fixed function to get runtime subdirectory path in utils

base <- read.csv(paste0(base.path, 'qalys.csv'))
support <- read.csv(paste0(support.path, 'qalys.csv'))
noSupport <- read.csv(paste0(noSupport.path, 'qalys.csv'))
```

@@

ggplot(combined.cost, aes(x = year, y = QALY_value, group = intervention, colour = intervention)) +
  geom_line()

combined.cost.change <- combined.cost %>%
  select(-total_boost, -QALYs) %>%
  pivot_wider(names_from = 'intervention',
              values_from = 'QALY_value') %>%
  mutate(change_Support = energyDownlift - baseline,
         change_NoSupport = energyDownliftNoSupport - baseline) %>%
  select(-baseline, -energyDownlift, -energyDownliftNoSupport) %>%
  pivot_longer(cols = -year,
               names_prefix = 'change_',
               names_to = 'intervention',
               values_to = 'value_change')

ggplot(combined.cost.change, aes(x = year, y = value_change, group = intervention, colour = intervention)) +
  geom_line()

@@

```{r}
total.combined.cost <- combined.cost %>%
  group_by(intervention) %>%
  summarise(total_value_change = sum(value_change))

@@

ICER <- combined.cost %>%
  pivot_wider(names_from = 'intervention',
              values_from = c('total_boost', 'QALYs', 'QALY_value')) %>%
  mutate(ICER_Support = (total_boost_energyDownlift - total_boost_baseline) / (QALYs_energyDownlift - QALYs_baseline),
         ICER_NoSupport = (total_boost_energyDownliftNoSupport - total_boost_baseline) / (QALYs_energyDownliftNoSupport - QALYs_baseline)) %>%
  select(year, ICER_Support, ICER_NoSupport) %>%
  pivot_longer(cols = -year,
               names_prefix = 'ICER_',
               names_to = 'intervention',
               values_to = 'ICER')

@@

ggplot(ICER.final, aes(x = intervention, y = ICER, group = intervention, fill = intervention, colour = intervention)) +
  geom_col()
```

>>>>

base <- read.csv(paste0(base.path, 'qalys.csv'))
support <- read.csv(paste0(support.path, 'qalys.csv'))
noSupport <- read.csv(paste0(noSupport.path, 'qalys.csv'))

# out.path <- '/home/luke/Documents/WORK/MINOS/PLOTS_FROM_ARC/QALY_TESTING/'
# 
# base <- read.csv(paste0(out.path, 'qaly_baseline.csv'))
# support <- read.csv(paste0(out.path, 'qalys_support.csv'))
# noSupport <- read.csv(paste0(out.path, 'qalys_noSupport.csv'))
```

@@

ggplot(combined.cost, aes(x = year, y = QALY_value, group = intervention, colour = intervention)) +
  geom_smooth()

combined.cost.change <- combined.cost %>%
  select(-total_boost, -QALYs) %>%
  pivot_wider(names_from = 'intervention',
              values_from = 'QALY_value') #%>%
  # mutate(change_Support = energyDownlift - baseline,
  #        change_NoSupport = energyDownliftNoSupport - baseline) %>%
  # select(-baseline, -energyDownlift, -energyDownliftNoSupport) %>%
  # pivot_longer(cols = -year,
  #              names_prefix = 'change_',
  #              names_to = 'intervention',
  #              values_to = 'value_change')

ggplot(combined.cost.change, aes(x = year, y = value_change, group = intervention, colour = intervention)) +
  geom_smooth()

@@

```{r}
combined.cost.mean <- combined.cost %>%
  group_by(year, intervention) %>%
  summarise(across(everything(), mean))

total.combined.cost <- combined.cost.change %>%
  group_by(intervention) %>%
  summarise(total_value_change = sum(value_change))

@@

ICER_test2 <- combined.cost.mean %>%
  pivot_wider(names_from = 'intervention',
              values_from = c('total_boost', 'QALYs', 'QALY_value')) %>%
  mutate(ICER_Support = (total_boost_energyDownlift - total_boost_baseline) / (QALYs_energyDownlift - QALYs_baseline),
         ICER_NoSupport = (total_boost_energyDownliftNoSupport - total_boost_baseline) / (QALYs_energyDownliftNoSupport - QALYs_baseline)) %>%
select(year, ICER_Support, ICER_NoSupport) %>%
  pivot_longer(cols = -year,
               names_prefix = 'ICER_',
               names_to = 'intervention',
               values_to = 'ICER')

@@

ggplot(ICER.final, aes(x = intervention, y = ICER, group = intervention, fill = intervention, colour = intervention)) +
  geom_col()

ICER_test3 <- combined.cost.mean %>%
  pivot_wider(names_from = 'intervention',
              values_from = c('total_boost', 'QALYs', 'QALY_value')) %>%
  mutate(C_Support = total_boost_energyDownlift - total_boost_baseline,
         E_Support = QALYs_energyDownlift - QALYs_baseline,
         C_NoSupport = total_boost_energyDownliftNoSupport - total_boost_baseline,
         E_NoSupport = QALYs_energyDownliftNoSupport - QALYs_baseline) %>%
  select(year, C_Support, E_Support, C_NoSupport, E_NoSupport) %>%
  mutate(ICER_Support = C_Support / E_Support,
         ICER_NoSupport = C_NoSupport / E_NoSupport)# %>%
  #select(year, ICER_Support, ICER_NoSupport)# %>%
#   pivot_longer(cols = -year,
#                names_prefix = 'ICER_',
#                names_to = 'intervention',
#                values_to = 'ICER')

```

```
